---
title: "250401_New_Wiggles"
author: "ezra amiri"
date: "4/7/2025"
output: html_document
---
# Clean Env & Load packages
```{r}
rm(list = ls()); gc()
```

```{r}
suppressPackageStartupMessages({
library(BSgenome.Calbipunctata.Cantata.uni4000)
library(SummarizedExperiment)
library(DESeq2)
library(DEGreport)
library(GenomicRanges)
library(GenomicAlignments)
library(GenomicFeatures)
library(Rsamtools)
library(tidyverse)
library(stringr)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(dplyr)
library(writexl)
library(readxl)
library(seqLogo)
library(ballgown)
library(Glimma)
library(Gviz)
library(zoo)
library(rtracklayer)
#library(topGO)
#library("apeglm")
#library(pheatmap)
#library(stats)
#library(beeswarm)
})
```


# Load data

# opa

## NC12 RNA-seq

```{r}
load("../GRanges/opakd-nc12-rnaseq.GRanges.R")

head(opakd.nc12.rnaseq)
```

## NC12 ATAC-seq
```{r}
load("../GRanges/opakd-nc12-openreads.GRanges.R")

head(opakd.nc12.openreads)
```

### NC12 updated coldata w/ genotypes
```{r}
nc12.opakd.coldata.atac <- as.data.frame(read_xlsx("../Processed_Data/250401/Results/opa/nc12-opa-coldata-updated.xlsx",sheet = 1))

nc12.opakd.coldata.atac %>% head()
```

```{r}
nc12.opakd.coldata.rna <- read_xlsx("../Processed_Data/250401/Results/opa/nc12-opa-coldata-updated.xlsx",sheet = 2)

nc12.opakd.coldata.rna %>% head()

```

## NC13 RNA-seq
```{r}
load("../GRanges/opakd-nc13-rnaseq.GRanges.R")

head(opakd.nc13.rnaseq)
```

## NC13 ATAC-seq
```{r}
load("../GRanges/opakd-nc13-openreads.GRanges.R")

head(opakd.nc13.openreads)
```

### NC13 updated coldatas w/ genotypes
```{r}
nc13.opakd.coldata.atac <- read_xlsx("../Processed_Data/250401/Results/opa/nc13-opa-coldata-updated.xlsx",sheet = 1)

nc13.opakd.coldata.atac %>% head()
```

```{r}
nc13.opakd.coldata.rna <- read_xlsx("../Processed_Data/250401/Results/opa/nc13-opa-coldata-updated.xlsx",sheet = 2)

nc13.opakd.coldata.rna %>% head()

```

# zld

## zld RNA-seq Data
```{r}
load("../GRanges/zldkd-rnaseq.GRanges.R")

head(zldkd.rnaseq)
```

## zld ATAC-seq Data
```{r}
load("../GRanges/zldkd-openreads.GRanges.R")

head(zldkd.openreads)
```

### Updated coldatas w/ genotypes
```{r}
zld.coldata.atac <- read_xlsx("../Processed_Data/250401/Results/zld/zld-coldata-updated.xlsx", sheet = 1)

zld.coldata.atac %>% head()
```

```{r}
zld.coldata.rna <- read_xlsx("../Processed_Data/250401/Results/zld/zld-coldata-updated.xlsx", sheet = 2)

zld.coldata.rna %>% head()
```


# TC ATAC

Open reads (<= 120 bp) for each sample individually
```{r}
load("../GRanges/wt-tc-openreads.GRanges.R")

#names(wt.tc.openreads)

#max(width(wt.tc.openreads))
```

# TC RNA 
Sample order: 1-4 NC2/3/maternal, 5-8 NC11, 9-12 NC12, 13-16 NC13, 17-20 NC14, 21-24 LNC14
```{r}
load("../GRanges/wt-tc-rnaseq.GRanges.R")

head(wt.tc.rnaseq)
```


# Check that the seqlevels, seqinfo etc match for all GRanges 
```{r}
seqlevels(opakd.nc12.rnaseq) == seqlevels(opakd.nc12.openreads) 

seqlevels(opakd.nc13.rnaseq) == seqlevels(opakd.nc13.openreads) 

seqlevels(zldkd.rnaseq) == seqlevels(zldkd.openreads) 

seqlevels(wt.tc.rnaseq) == seqlevels(wt.tc.openreads) 

all(seqlevels(opakd.nc12.rnaseq) == seqlevels(opakd.nc13.rnaseq) & seqlevels(opakd.nc12.rnaseq) == seqlevels(zldkd.rnaseq) & seqlevels(opakd.nc12.rnaseq) == seqlevels(wt.tc.rnaseq))

all(seqlevels(opakd.nc12.openreads) == seqlevels(opakd.nc13.openreads) & seqlevels(opakd.nc12.openreads) == seqlevels(zldkd.openreads) & seqlevels(opakd.nc12.openreads) == seqlevels(wt.tc.openreads))

seqlevels(opakd.nc12.openreads)

```
```{r}

seqinfo(opakd.nc12.openreads)
seqinfo(opakd.nc12.rnaseq) 
seqinfo(opakd.nc13.openreads)
seqinfo(opakd.nc13.rnaseq) 
seqinfo(zldkd.rnaseq)
seqinfo(zldkd.openreads)
seqinfo(wt.tc.rnaseq) 
seqinfo(wt.tc.openreads)

```

Two GRanges do not have the genome column set to Clogmia ca6. Update below
```{r}
genome(zldkd.rnaseq) <- "ca6"
genome(wt.tc.openreads) <- "ca6"
```

# Create a tiled version of the genome

This is used to bin reads into, using the binnedAverage function.
```{r}
ca.10bp <- tileGenome(seqlengths(BSgenome.Calbipunctata.Cantata.uni4000), tilewidth = 10, cut.last.tile.in.chrom = TRUE)
```

## update seqlevels and seqinfo and seqlevelsinuse for tiled genome ca.10bp
If seqlevels do not match binnedAverage will not work.
```{r}
good.uns <- seqlevels(wt.tc.openreads)
good.uns
```

```{r}
ca.10bp <- ca.10bp[seqnames(ca.10bp) %in% good.uns]
seqlevels(ca.10bp) <- seqlevels(wt.tc.openreads)
seqinfo(ca.10bp) <- seqinfo(wt.tc.openreads)
seqlevels(ca.10bp) <- seqlevelsInUse(ca.10bp)
```

# Make bigWig/Wiggles

## opa NC12 RNA-seq Inv Samples

Binned Average
```{r}
opakd.nc12.rna.ba <- lapply(opakd.nc12.rnaseq, function(x){
  a = binnedAverage(bins = ca.10bp, numvar = coverage(x), varname = 'score')
  })
```

CPM normalized score

Get length(number of reads) for each sample 
```{r}
lens.opakd.nc12.rnaseq <- lengths(opakd.nc12.rnaseq)
#lens.opakd.nc12.rnaseq
```

Divide the score by the number of reads then * 1M
```{r}
for(i in 1 : length(opakd.nc12.rna.ba)){score(opakd.nc12.rna.ba[[i]]) = signif(score(opakd.nc12.rna.ba[[i]])/lens.opakd.nc12.rnaseq[i]*1e+6, 4)}
```

Export path

Make a vector of file paths for each sample 
```{r}
file.names <- gsub(pattern = "\\.", replacement = "-", names(opakd.nc12.rna.ba))
                   
export.path <- paste0("../Processed_Data/Wiggles/opa/RNA/NC12/",file.names,".bw")

head(export.path)
#export.path
```


```{r}
export(opakd.nc12.rna.ba[[3]], con = export.path[3], format = 'bigWig')
```

```{r}
for(i in 1:8){export(opakd.nc12.rna.ba[[i]], con = export.path[i], format = 'bigWig')}
```

```{r}
for(i in 9:15){export(opakd.nc12.rna.ba[[i]], con = export.path[i], format = 'bigWig')}
```

## opa NC12 RNA-seq merged by genotype

```{r}
nc12.opa.samples.rna.names <- nc12.opakd.coldata.rna %>% filter(genotype == "opa") %>% select(row.name)
#nc12.opa.samples.rna.names
nc12.opa.rna.merged <- sort(unlist(opakd.nc12.rnaseq[names(opakd.nc12.rnaseq) %in% nc12.opa.samples.rna.names$row.name]))

nc12.ac.samples.rna.names <- nc12.opakd.coldata.rna %>% filter(genotype == "ac") %>% select(row.name)
#nc12.ac.samples.rna.names
nc12.ac.rna.merged <- sort(unlist(opakd.nc12.rnaseq[names(opakd.nc12.rnaseq) %in% nc12.ac.samples.rna.names$row.name]))

nc12.dsred.samples.rna.names <- nc12.opakd.coldata.rna %>% filter(genotype == "dsred") %>% select(row.name)
#nc12.dsred.samples.rna.names
nc12.dsred.rna.merged <- sort(unlist(opakd.nc12.rnaseq[names(opakd.nc12.rnaseq) %in% nc12.dsred.samples.rna.names$row.name]))

nc12.wt.samples.rna.names <- nc12.opakd.coldata.rna %>% filter(genotype == "wt") %>% select(row.name)
#nc12.wt.samples.rna.names
nc12.wt.rna.merged <- sort(unlist(opakd.nc12.rnaseq[names(opakd.nc12.rnaseq) %in% nc12.wt.samples.rna.names$row.name]))

nc12.noKD.samples.rna.names <- nc12.opakd.coldata.rna %>% filter(genotype == "noKD") %>% select(row.name)
#nc12.noKD.samples.rna.names
nc12.noKD.rna.merged <- sort(unlist(opakd.nc12.rnaseq[names(opakd.nc12.rnaseq) %in% nc12.noKD.samples.rna.names$row.name]))

nc12.intKD.samples.rna.names <- nc12.opakd.coldata.rna %>% filter(genotype == "intKD") %>% select(row.name)
#nc12.intKD.samples.rna.names
nc12.intKD.rna.merged <- sort(unlist(opakd.nc12.rnaseq[names(opakd.nc12.rnaseq) %in% nc12.intKD.samples.rna.names$row.name]))

```

Binned Average
```{r}
nc12.opa.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.opa.rna.merged), varname = 'score')

nc12.ac.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.ac.rna.merged), varname = 'score')

nc12.dsred.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.dsred.rna.merged), varname = 'score')

nc12.wt.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.wt.rna.merged), varname = 'score')

nc12.noKD.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.noKD.rna.merged), varname = 'score')

nc12.intKD.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.intKD.rna.merged), varname = 'score')

```

CPM Normalize 
```{r}
score(nc12.opa.rna.ba) <- signif(score(nc12.opa.rna.ba)/length(nc12.opa.rna.merged)*1e+6, 4)

score(nc12.ac.rna.ba) <- signif(score(nc12.ac.rna.ba)/length(nc12.ac.rna.merged)*1e+6, 4)

score(nc12.dsred.rna.ba) <- signif(score(nc12.dsred.rna.ba)/length(nc12.dsred.rna.merged)*1e+6, 4)

score(nc12.wt.rna.ba) <- signif(score(nc12.wt.rna.ba)/length(nc12.wt.rna.merged)*1e+6, 4)

score(nc12.noKD.rna.ba) <- signif(score(nc12.noKD.rna.ba)/length(nc12.noKD.rna.merged)*1e+6, 4)

score(nc12.intKD.rna.ba) <- signif(score(nc12.intKD.rna.ba)/length(nc12.intKD.rna.merged)*1e+6, 4)

```

Export
```{r}
export(object = nc12.opa.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC12/opa-nc12-rna-merged.bw", format = "bigWig")

export(object = nc12.ac.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC12/ac-nc12-rna-merged.bw", format = "bigWig")

export(object = nc12.dsred.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC12/dsred-nc12-rna-merged.bw", format = "bigWig")

export(object = nc12.wt.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC12/wt-nc12-rna-merged.bw", format = "bigWig")

export(object = nc12.noKD.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC12/noKD-nc12-rna-merged.bw", format = "bigWig")

export(object = nc12.intKD.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC12/intKD-nc12-rna-merged.bw", format = "bigWig")
```

## opa NC12 ATAC-seq Inv samples

Binned Average
```{r}
opakd.nc12.atac.ba <- lapply(opakd.nc12.openreads, function(x){
  a = binnedAverage(bins = ca.10bp, numvar = coverage(x), varname = 'score')
  })
```

CPM normalized score

Get length (number of reads) for each sample 
```{r}
lens.opakd.nc12.atac <- lengths(opakd.nc12.openreads)
#lens.opakd.nc12.atac
```

Divide the score by the number of reads then * 1M
```{r}
for(i in 1 : length(opakd.nc12.atac.ba)){score(opakd.nc12.atac.ba[[i]]) = signif(score(opakd.nc12.atac.ba[[i]])/lens.opakd.nc12.atac[i]*1e+6, 4)}
```

Export path

Make a vector of file paths for each sample 
```{r}
file.names <- gsub(pattern = "\\.", replacement = "-", names(opakd.nc12.atac.ba))
                   
export.path <- paste0("../Processed_Data/Wiggles/opa/ATAC/NC12/",file.names,".bw")

head(export.path)
#export.path
```

```{r}
for(i in 1:8){export(opakd.nc12.atac.ba[[i]], con = export.path[i], format = 'bigWig')}
```


```{r}
for(i in 9:15){export(opakd.nc12.atac.ba[[i]], con = export.path[i], format = 'bigWig')}
```

## opa NC12 ATAC-seq merged by genotype

```{r}
nc12.opa.samples.atac.names <- nc12.opakd.coldata.atac %>% filter(genotype == "opa") %>% select(row.name)
#nc12.opa.samples.atac.names
nc12.opa.atac.merged <- sort(unlist(opakd.nc12.openreads[names(opakd.nc12.openreads) %in% nc12.opa.samples.atac.names$row.name]))

nc12.ac.samples.atac.names <- nc12.opakd.coldata.atac %>% filter(genotype == "ac") %>% select(row.name)
#nc12.ac.samples.atac.names
nc12.ac.atac.merged <- sort(unlist(opakd.nc12.openreads[names(opakd.nc12.openreads) %in% nc12.ac.samples.atac.names$row.name]))

nc12.dsred.samples.atac.names <- nc12.opakd.coldata.atac %>% filter(genotype == "dsred") %>% select(row.name)
#nc12.dsred.samples.atac.names
nc12.dsred.atac.merged <- sort(unlist(opakd.nc12.openreads[names(opakd.nc12.openreads) %in% nc12.dsred.samples.atac.names$row.name]))

nc12.wt.samples.atac.names <- nc12.opakd.coldata.atac %>% filter(genotype == "wt") %>% select(row.name)
#nc12.wt.samples.atac.names
nc12.wt.atac.merged <- sort(unlist(opakd.nc12.openreads[names(opakd.nc12.openreads) %in% nc12.wt.samples.atac.names$row.name]))

nc12.noKD.samples.atac.names <- nc12.opakd.coldata.atac %>% filter(genotype == "noKD") %>% select(row.name)
#nc12.noKD.samples.atac.names
nc12.noKD.atac.merged <- sort(unlist(opakd.nc12.openreads[names(opakd.nc12.openreads) %in% nc12.noKD.samples.atac.names$row.name]))

nc12.intKD.samples.atac.names <- nc12.opakd.coldata.atac %>% filter(genotype == "intKD") %>% select(row.name)
#nc12.intKD.samples.atac.names
nc12.intKD.atac.merged <- sort(unlist(opakd.nc12.openreads[names(opakd.nc12.openreads) %in% nc12.intKD.samples.atac.names$row.name]))

```

Binned Average
```{r}
nc12.opa.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.opa.atac.merged), varname = 'score')

nc12.ac.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.ac.atac.merged), varname = 'score')

nc12.dsred.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.dsred.atac.merged), varname = 'score')

nc12.wt.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.wt.atac.merged), varname = 'score')

nc12.noKD.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.noKD.atac.merged), varname = 'score')

nc12.intKD.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.intKD.atac.merged), varname = 'score')

```

CPM Normalize 
```{r}
score(nc12.opa.atac.ba) <- signif(score(nc12.opa.atac.ba)/length(nc12.opa.atac.merged)*1e+6, 4)

score(nc12.ac.atac.ba) <- signif(score(nc12.ac.atac.ba)/length(nc12.ac.atac.merged)*1e+6, 4)

score(nc12.dsred.atac.ba) <- signif(score(nc12.dsred.atac.ba)/length(nc12.dsred.atac.merged)*1e+6, 4)

score(nc12.wt.atac.ba) <- signif(score(nc12.wt.atac.ba)/length(nc12.wt.atac.merged)*1e+6, 4)

score(nc12.noKD.atac.ba) <- signif(score(nc12.noKD.atac.ba)/length(nc12.noKD.atac.merged)*1e+6, 4)

score(nc12.intKD.atac.ba) <- signif(score(nc12.intKD.atac.ba)/length(nc12.intKD.atac.merged)*1e+6, 4)

```

Export
```{r}
export(object = nc12.opa.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC12/opa-nc12-atac-merged.bw", format = "bigWig")

export(object = nc12.ac.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC12/ac-nc12-atac-merged.bw", format = "bigWig")

export(object = nc12.dsred.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC12/dsred-nc12-atac-merged.bw", format = "bigWig")

export(object = nc12.wt.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC12/wt-nc12-atac-merged.bw", format = "bigWig")

export(object = nc12.noKD.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC12/noKD-nc12-atac-merged.bw", format = "bigWig")

export(object = nc12.intKD.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC12/intKD-nc12-atac-merged.bw", format = "bigWig")
```



## opa NC13 RNA-seq Inv Samples

Binned Average
```{r}
opakd.nc13.rna.ba <- lapply(opakd.nc13.rnaseq, function(x){
  a = binnedAverage(bins = ca.10bp, numvar = coverage(x), varname = 'score')
  })
```

CPM normalized score

Get length (number of reads) for each sample 
```{r}
lens.opakd.nc13.rnaseq <- lengths(opakd.nc13.rnaseq)
#lens.opakd.nc13.rnaseq
```

Divide the score by the number of reads then * 1M
```{r}
for(i in 1 : length(opakd.nc13.rna.ba)){score(opakd.nc13.rna.ba[[i]]) = signif(score(opakd.nc13.rna.ba[[i]])/lens.opakd.nc13.rnaseq[i]*1e+6, 4)}
```

Export path

Make a vector of file paths for each sample 
```{r}
file.names <- gsub(pattern = "\\.", replacement = "-", names(opakd.nc13.rna.ba))
                   
export.path <- paste0("../Processed_Data/Wiggles/opa/RNA/NC13/",file.names,".bw")

head(export.path)
#export.path
```

```{r}
for(i in 1:9){export(opakd.nc13.rna.ba[[i]], con = export.path[i], format = 'bigWig')}
```


```{r}
for(i in 10:18){export(opakd.nc13.rna.ba[[i]], con = export.path[i], format = 'bigWig')}
```

## opa NC13 RNA-seq merged by genotype

```{r}
nc13.opa.samples.rna.names <- nc13.opakd.coldata.rna %>% filter(genotype == "opa") %>% select(row.name)
#nc13.opa.samples.rna.names
nc13.opa.rna.merged <- sort(unlist(opakd.nc13.rnaseq[names(opakd.nc13.rnaseq) %in% nc13.opa.samples.rna.names$row.name]))

nc13.ac.samples.rna.names <- nc13.opakd.coldata.rna %>% filter(genotype == "ac") %>% select(row.name)
#nc13.ac.samples.rna.names
nc13.ac.rna.merged <- sort(unlist(opakd.nc13.rnaseq[names(opakd.nc13.rnaseq) %in% nc13.ac.samples.rna.names$row.name]))

nc13.dsred.samples.rna.names <- nc13.opakd.coldata.rna %>% filter(genotype == "dsred") %>% select(row.name)
#nc13.dsred.samples.rna.names
nc13.dsred.rna.merged <- sort(unlist(opakd.nc13.rnaseq[names(opakd.nc13.rnaseq) %in% nc13.dsred.samples.rna.names$row.name]))

nc13.wt.samples.rna.names <- nc13.opakd.coldata.rna %>% filter(genotype == "wt") %>% select(row.name)
#nc13.wt.samples.rna.names
nc13.wt.rna.merged <- sort(unlist(opakd.nc13.rnaseq[names(opakd.nc13.rnaseq) %in% nc13.wt.samples.rna.names$row.name]))

nc13.noKD.samples.rna.names <- nc13.opakd.coldata.rna %>% filter(genotype == "noKD") %>% select(row.name)
#nc13.noKD.samples.rna.names
nc13.noKD.rna.merged <- sort(unlist(opakd.nc13.rnaseq[names(opakd.nc13.rnaseq) %in% nc13.noKD.samples.rna.names$row.name]))

nc13.intKD.samples.rna.names <- nc13.opakd.coldata.rna %>% filter(genotype == "intKD") %>% select(row.name)
#nc13.intKD.samples.rna.names
nc13.intKD.rna.merged <- sort(unlist(opakd.nc13.rnaseq[names(opakd.nc13.rnaseq) %in% nc13.intKD.samples.rna.names$row.name]))

```

Binned Average
```{r}
nc13.opa.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.opa.rna.merged), varname = 'score')

nc13.ac.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.ac.rna.merged), varname = 'score')

nc13.dsred.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.dsred.rna.merged), varname = 'score')

nc13.wt.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.wt.rna.merged), varname = 'score')

nc13.noKD.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.noKD.rna.merged), varname = 'score')

nc13.intKD.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.intKD.rna.merged), varname = 'score')

```

CPM Normalize 
```{r}
score(nc13.opa.rna.ba) <- signif(score(nc13.opa.rna.ba)/length(nc13.opa.rna.merged)*1e+6, 4)

score(nc13.ac.rna.ba) <- signif(score(nc13.ac.rna.ba)/length(nc13.ac.rna.merged)*1e+6, 4)

score(nc13.dsred.rna.ba) <- signif(score(nc13.dsred.rna.ba)/length(nc13.dsred.rna.merged)*1e+6, 4)

score(nc13.wt.rna.ba) <- signif(score(nc13.wt.rna.ba)/length(nc13.wt.rna.merged)*1e+6, 4)

score(nc13.noKD.rna.ba) <- signif(score(nc13.noKD.rna.ba)/length(nc13.noKD.rna.merged)*1e+6, 4)

score(nc13.intKD.rna.ba) <- signif(score(nc13.intKD.rna.ba)/length(nc13.intKD.rna.merged)*1e+6, 4)

```

Export
```{r}
export(object = nc13.opa.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC13/opa-nc13-rna-merged.bw", format = "bigWig")

export(object = nc13.ac.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC13/ac-nc13-rna-merged.bw", format = "bigWig")

export(object = nc13.dsred.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC13/dsred-nc13-rna-merged.bw", format = "bigWig")

export(object = nc13.wt.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC13/wt-nc13-rna-merged.bw", format = "bigWig")

export(object = nc13.noKD.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC13/noKD-nc13-rna-merged.bw", format = "bigWig")

export(object = nc13.intKD.rna.ba, con = "../Processed_Data/Wiggles/opa/RNA/NC13/intKD-nc13-rna-merged.bw", format = "bigWig")
```

## opa NC13 ATAC-seq Inv samples

Binned Average
```{r}
opakd.nc13.atac.ba <- lapply(opakd.nc13.openreads, function(x){
  a = binnedAverage(bins = ca.10bp, numvar = coverage(x), varname = 'score')
  })
```

CPM normalized score

Get length (number of reads) for each sample 
```{r}
lens.opakd.nc13.atac <- lengths(opakd.nc13.openreads)
#lens.opakd.nc13.atac
```

Divide the score by the number of reads then * 1M
```{r}
for(i in 1 : length(opakd.nc13.atac.ba)){score(opakd.nc13.atac.ba[[i]]) = signif(score(opakd.nc13.atac.ba[[i]])/lens.opakd.nc13.atac[i]*1e+6, 4)}
```

Export path

Make a vector of file paths for each sample 
```{r}
file.names <- gsub(pattern = "\\.", replacement = "-", names(opakd.nc13.atac.ba))
                   
export.path <- paste0("../Processed_Data/Wiggles/opa/ATAC/NC13/",file.names,".bw")

head(export.path)
#export.path
```

```{r}
for(i in 1:9){export(opakd.nc13.atac.ba[[i]], con = export.path[i], format = 'bigWig')}
```


```{r}
#for(i in 10:18){export(opakd.nc13.atac.ba[[i]], con = export.path[i], format = 'bigWig')}


export(opakd.nc13.atac.ba[[10]], con = export.path[10], format = 'bigWig')

export(opakd.nc13.atac.ba[[11]], con = export.path[11], format = 'bigWig')

export(opakd.nc13.atac.ba[[12]], con = export.path[12], format = 'bigWig')

export(opakd.nc13.atac.ba[[13]], con = export.path[13], format = 'bigWig')

export(opakd.nc13.atac.ba[[14]], con = export.path[14], format = 'bigWig')

export(opakd.nc13.atac.ba[[15]], con = export.path[15], format = 'bigWig')

export(opakd.nc13.atac.ba[[16]], con = export.path[16], format = 'bigWig')

export(opakd.nc13.atac.ba[[17]], con = export.path[17], format = 'bigWig')

export(opakd.nc13.atac.ba[[18]], con = export.path[18], format = 'bigWig')


```

## opa NC13 ATAC-seq merged by genotype

```{r}
nc13.opa.samples.atac.names <- nc13.opakd.coldata.atac %>% filter(genotype == "opa") %>% select(row.name)
#nc13.opa.samples.atac.names
nc13.opa.atac.merged <- sort(unlist(opakd.nc13.openreads[names(opakd.nc13.openreads) %in% nc13.opa.samples.atac.names$row.name]))

nc13.ac.samples.atac.names <- nc13.opakd.coldata.atac %>% filter(genotype == "ac") %>% select(row.name)
#nc13.ac.samples.atac.names
nc13.ac.atac.merged <- sort(unlist(opakd.nc13.openreads[names(opakd.nc13.openreads) %in% nc13.ac.samples.atac.names$row.name]))

nc13.dsred.samples.atac.names <- nc13.opakd.coldata.atac %>% filter(genotype == "dsred") %>% select(row.name)
#nc13.dsred.samples.atac.names
nc13.dsred.atac.merged <- sort(unlist(opakd.nc13.openreads[names(opakd.nc13.openreads) %in% nc13.dsred.samples.atac.names$row.name]))

nc13.wt.samples.atac.names <- nc13.opakd.coldata.atac %>% filter(genotype == "wt") %>% select(row.name)
#nc13.wt.samples.atac.names
nc13.wt.atac.merged <- sort(unlist(opakd.nc13.openreads[names(opakd.nc13.openreads) %in% nc13.wt.samples.atac.names$row.name]))

nc13.noKD.samples.atac.names <- nc13.opakd.coldata.atac %>% filter(genotype == "noKD") %>% select(row.name)
#nc13.noKD.samples.atac.names
nc13.noKD.atac.merged <- sort(unlist(opakd.nc13.openreads[names(opakd.nc13.openreads) %in% nc13.noKD.samples.atac.names$row.name]))

nc13.intKD.samples.atac.names <- nc13.opakd.coldata.atac %>% filter(genotype == "intKD") %>% select(row.name)
#nc13.intKD.samples.atac.names
nc13.intKD.atac.merged <- sort(unlist(opakd.nc13.openreads[names(opakd.nc13.openreads) %in% nc13.intKD.samples.atac.names$row.name]))

```

Binned Average
```{r}
nc13.opa.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.opa.atac.merged), varname = 'score')

nc13.ac.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.ac.atac.merged), varname = 'score')

nc13.dsred.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.dsred.atac.merged), varname = 'score')

nc13.wt.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.wt.atac.merged), varname = 'score')

nc13.noKD.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.noKD.atac.merged), varname = 'score')

nc13.intKD.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.intKD.atac.merged), varname = 'score')

```

CPM Normalize 
```{r}
score(nc13.opa.atac.ba) <- signif(score(nc13.opa.atac.ba)/length(nc13.opa.atac.merged)*1e+6, 4)

score(nc13.ac.atac.ba) <- signif(score(nc13.ac.atac.ba)/length(nc13.ac.atac.merged)*1e+6, 4)

score(nc13.dsred.atac.ba) <- signif(score(nc13.dsred.atac.ba)/length(nc13.dsred.atac.merged)*1e+6, 4)

score(nc13.wt.atac.ba) <- signif(score(nc13.wt.atac.ba)/length(nc13.wt.atac.merged)*1e+6, 4)

score(nc13.noKD.atac.ba) <- signif(score(nc13.noKD.atac.ba)/length(nc13.noKD.atac.merged)*1e+6, 4)

score(nc13.intKD.atac.ba) <- signif(score(nc13.intKD.atac.ba)/length(nc13.intKD.atac.merged)*1e+6, 4)

```

Export
```{r}
export(object = nc13.opa.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC13/opa-nc13-atac-merged.bw", format = "bigWig")

export(object = nc13.ac.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC13/ac-nc13-atac-merged.bw", format = "bigWig")

export(object = nc13.dsred.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC13/dsred-nc13-atac-merged.bw", format = "bigWig")

export(object = nc13.wt.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC13/wt-nc13-atac-merged.bw", format = "bigWig")

export(object = nc13.noKD.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC13/noKD-nc12-atac-merged.bw", format = "bigWig")

export(object = nc13.intKD.atac.ba, con = "../Processed_Data/Wiggles/opa/ATAC/NC13/intKD-nc13-atac-merged.bw", format = "bigWig")
```


## zld RNA-seq Inv samples

Binned Average
```{r}
zldkd.rna.ba <- lapply(zldkd.rnaseq, function(x){
  a = binnedAverage(bins = ca.10bp, numvar = coverage(x), varname = 'score')
  })
```

CPM normalized score

Get length (number of reads) for each sample 
```{r}
lens.zldkd.rnaseq <- lengths(zldkd.rnaseq)

#lens.zldkd.rnaseq

```

Divide the score by the number of reads then * 1M
```{r}
for(i in 1 : length(zldkd.rna.ba)){score(zldkd.rna.ba[[i]]) =signif(score(zldkd.rna.ba[[i]])/lens.zldkd.rnaseq[i]*1e+6, 4)}
```


Export path

Make a vector of file paths for each sample 
```{r}
file.names <- gsub(pattern = "\\.", replacement = "-", names(zldkd.rna.ba))
#file.names                   
export.path <- paste0("../Processed_Data/Wiggles/zld/RNA/",file.names,".bw")

#export.path
```

```{r}
for(i in 1:9){export(zldkd.rna.ba[[i]], con = export.path[i], format = 'bigWig')}
```


```{r}
for(i in 10:18){export(zldkd.rna.ba[[i]], con = export.path[i], format = 'bigWig')}
```


## zld RNA-seq merged by genotype

```{r}
zld.samples.rna.names <- zld.coldata.rna %>% filter(genotype == "zld") %>% select(row.name)
#zld.samples.rna.names
zld.rna.merged <- sort(unlist(zldkd.rnaseq[names(zldkd.rnaseq) %in% zld.samples.rna.names$row.name]))

ac.samples.rna.names <- zld.coldata.rna %>% filter(genotype == "ac") %>% select(row.name)
#ac.samples.rna.names
ac.rna.merged <- sort(unlist(zldkd.rnaseq[names(zldkd.rnaseq) %in% ac.samples.rna.names$row.name]))

wt.samples.rna.names <- zld.coldata.rna %>% filter(genotype == "wt") %>% select(row.name)
#wt.samples.rna.names
wt.rna.merged <- sort(unlist(zldkd.rnaseq[names(zldkd.rnaseq) %in% wt.samples.rna.names$row.name]))

noKD.samples.rna.names <- zld.coldata.rna %>% filter(genotype == "noKD") %>% select(row.name)
#noKD.samples.rna.names
noKD.rna.merged <- sort(unlist(zldkd.rnaseq[names(zldkd.rnaseq) %in% noKD.samples.rna.names$row.name]))

intKD.samples.rna.names <- zld.coldata.rna %>% filter(genotype == "intKD") %>% select(row.name)
#intKD.samples.rna.names
intKD.rna.merged <- sort(unlist(zldkd.rnaseq[names(zldkd.rnaseq) %in% intKD.samples.rna.names$row.name]))

```


Binned Average
```{r}
zld.rna.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(zld.rna.merged), varname = 'score')

ac.rna.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(ac.rna.merged), varname = 'score')

wt.rna.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(wt.rna.merged), varname = 'score')

noKD.rna.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(noKD.rna.merged), varname = 'score')

intKD.rna.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(intKD.rna.merged), varname = 'score')
```

CPM Normalize 
```{r}
score(zld.rna.merged.ba) <- signif(score(zld.rna.merged.ba)/length(zld.rna.merged)*1e+6, 4)

score(ac.rna.merged.ba) <- signif(score(ac.rna.merged.ba)/length(ac.rna.merged)*1e+6, 4)

score(wt.rna.merged.ba) <- signif(score(wt.rna.merged.ba)/length(wt.rna.merged)*1e+6, 4)

score(noKD.rna.merged.ba) <- signif(score(noKD.rna.merged.ba)/length(noKD.rna.merged)*1e+6, 4)

score(intKD.rna.merged.ba) <- signif(score(intKD.rna.merged.ba)/length(intKD.rna.merged)*1e+6, 4)

```

Export
```{r}
export(object = zld.rna.merged.ba, con = "../Processed_Data/Wiggles/zld/RNA/zld-rna-merged.bw", format = "bigWig")

export(object = ac.rna.merged.ba, con = "../Processed_Data/Wiggles/zld/RNA/ac-rna-merged.bw", format = "bigWig")


export(object = wt.rna.merged.ba, con = "../Processed_Data/Wiggles/zld/RNA/wt-rna-merged.bw", format = "bigWig")

export(object = noKD.rna.merged.ba, con = "../Processed_Data/Wiggles/zld/RNA/noKD-rna-merged.bw", format = "bigWig")

export(object = intKD.rna.merged.ba, con = "../Processed_Data/Wiggles/zld/RNA/intKD-rna-merged.bw", format = "bigWig")
```

## zld ATAC-seq Inv samples

Binned Average
```{r}
zldkd.atac.ba <- lapply(zldkd.openreads, function(x){
  a = binnedAverage(bins = ca.10bp, numvar = coverage(x), varname = 'score')
  })
```

CPM normalized score

Get length (number of reads) for each sample 
```{r}
lens.zldkd.atac <- lengths(zldkd.openreads)
#lens.zldkd.atac

```

Divide the score by the number of reads then * 1M
```{r}
for(i in 1 : length(zldkd.atac.ba)){score(zldkd.atac.ba[[i]]) =signif(score(zldkd.atac.ba[[i]])/lens.zldkd.atac[i]*1e+6, 4)}
```


Export path

Make a vector of file paths for each sample 
```{r}
file.names <- gsub(pattern = "\\.", replacement = "-", names(zldkd.atac.ba))
#file.names                   
export.path <- paste0("../Processed_Data/Wiggles/zld/ATAC/",file.names,".bw")

export.path
```

```{r}
for(i in 1:9){export(zldkd.atac.ba[[i]], con = export.path[i], format = 'bigWig')}
```


```{r}
for(i in 10:18){export(zldkd.atac.ba[[i]], con = export.path[i], format = 'bigWig')}
```


## zld ATAC-seq merged by genotype

```{r}
zld.samples.atac.names <- zld.coldata.atac %>% filter(genotype == "zld") %>% select(row.name)
#zld.samples.atac.names
zld.atac.merged <- sort(unlist(zldkd.openreads[names(zldkd.openreads) %in% zld.samples.atac.names$row.name]))

ac.samples.atac.names <- zld.coldata.atac %>% filter(genotype == "ac") %>% select(row.name)
#ac.samples.atac.names
ac.atac.merged <- sort(unlist(zldkd.openreads[names(zldkd.openreads) %in% ac.samples.atac.names$row.name]))

wt.samples.atac.names <- zld.coldata.atac %>% filter(genotype == "wt") %>% select(row.name)
#wt.samples.atac.names
wt.atac.merged <- sort(unlist(zldkd.openreads[names(zldkd.openreads) %in% wt.samples.atac.names$row.name]))

noKD.samples.atac.names <- zld.coldata.atac %>% filter(genotype == "noKD") %>% select(row.name)
#noKD.samples.atac.names
noKD.atac.merged <- sort(unlist(zldkd.openreads[names(zldkd.openreads) %in% noKD.samples.atac.names$row.name]))

intKD.samples.atac.names <- zld.coldata.atac %>% filter(genotype == "intKD") %>% select(row.name)
#intKD.samples.atac.names
intKD.atac.merged <- sort(unlist(zldkd.openreads[names(zldkd.openreads) %in% intKD.samples.atac.names$row.name]))

```


Binned Average
```{r}
zld.atac.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(zld.atac.merged), varname = 'score')

ac.atac.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(ac.atac.merged), varname = 'score')

wt.atac.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(wt.atac.merged), varname = 'score')

noKD.atac.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(noKD.atac.merged), varname = 'score')

intKD.atac.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(intKD.atac.merged), varname = 'score')
```

CPM Normalize 
```{r}
score(zld.atac.merged.ba) <- signif(score(zld.atac.merged.ba)/length(zld.atac.merged)*1e+6, 4)

score(ac.atac.merged.ba) <- signif(score(ac.atac.merged.ba)/length(ac.atac.merged)*1e+6, 4)

score(wt.atac.merged.ba) <- signif(score(wt.atac.merged.ba)/length(wt.atac.merged)*1e+6, 4)

score(noKD.atac.merged.ba) <- signif(score(noKD.atac.merged.ba)/length(noKD.atac.merged)*1e+6, 4)

score(intKD.atac.merged.ba) <- signif(score(intKD.atac.merged.ba)/length(intKD.atac.merged)*1e+6, 4)

```

Export
```{r}
export(object = zld.atac.merged.ba, con = "../Processed_Data/Wiggles/zld/ATAC/zld-atac-merged.bw", format = "bigWig")

export(object = ac.atac.merged.ba, con = "../Processed_Data/Wiggles/zld/ATAC/ac-atac-merged.bw", format = "bigWig")


export(object = wt.atac.merged.ba, con = "../Processed_Data/Wiggles/zld/ATAC/wt-atac-merged.bw", format = "bigWig")

export(object = noKD.atac.merged.ba, con = "../Processed_Data/Wiggles/zld/ATAC/noKD-atac-merged.bw", format = "bigWig")

export(object = intKD.atac.merged.ba, con = "../Processed_Data/Wiggles/zld/ATAC/intKD-atac-merged.bw", format = "bigWig")
```



## ATAC-seq timecourse

all open reads
```{r}
all.openreads.merged <- sort(unlist(wt.tc.openreads))

names(all.openreads.merged)  <- NULL
```

Sort by stage 
```{r}
nc11.openreads.merged <-
  sort(unlist(wt.tc.openreads[grepl(names(wt.tc.openreads), pattern = "\\.NC11\\.")]))

nc12.openreads.merged <- sort(unlist(wt.tc.openreads[grepl(names(wt.tc.openreads), pattern = "\\.NC12\\.")]))

nc13.openreads.merged <- sort(unlist(wt.tc.openreads[grepl(names(wt.tc.openreads), pattern = "\\.NC13\\.")]))

nc14.openreads.merged <- sort(unlist(wt.tc.openreads[grepl(names(wt.tc.openreads), pattern = "\\.NC14\\.")]))

lnc14.openreads.merged <-
  sort(unlist(wt.tc.openreads[grepl(names(wt.tc.openreads), pattern = "\\.LNC14\\.")]))
```


```{r}
names(nc11.openreads.merged) <- NULL

names(nc12.openreads.merged) <- NULL

names(nc13.openreads.merged) <- NULL

names(nc14.openreads.merged) <- NULL

names(lnc14.openreads.merged) <- NULL

```


Bin Average all open reads 
```{r}
all.openreads.merged.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(all.openreads.merged), varname = 'score')
```

Bin average open reads merged by stage
```{r}
nc11.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc11.openreads.merged), varname = 'score')
nc12.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.openreads.merged), varname = 'score')
nc13.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.openreads.merged), varname = 'score')
nc14.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc14.openreads.merged), varname = 'score')
lnc14.atac.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(lnc14.openreads.merged), varname = 'score')
```


CPM normalize all open reads
```{r}
score(all.openreads.merged.ba) <- signif(score(all.openreads.merged.ba)/length(all.openreads.merged)*1e+6, 4)
```

CPM normalize merged by stage
```{r}
score(nc11.atac.ba) <- signif(score(nc11.atac.ba)/length(nc11.openreads.merged)*1e+6, 4)
score(nc12.atac.ba) <- signif(score(nc12.atac.ba)/length(nc12.openreads.merged)*1e+6, 4)
score(nc13.atac.ba) <- signif(score(nc13.atac.ba)/length(nc13.openreads.merged)*1e+6, 4)
score(nc14.atac.ba) <- signif(score(nc14.atac.ba)/length(nc14.openreads.merged)*1e+6, 4)
score(lnc14.atac.ba) <- signif(score(lnc14.atac.ba)/length(lnc14.openreads.merged)*1e+6, 4)
```


Export
```{r}
export(all.openreads.merged.ba, con = "../Processed_Data/Wiggles/ATAC/WT_TC/all-atac-merged.bw", format = 'bigWig')

export(nc11.atac.ba, con = "../Processed_Data/Wiggles/ATAC/WT_TC/nc11-atac.bw", format = 'bigWig')

export(nc12.atac.ba, con = "../Processed_Data/Wiggles/ATAC/WT_TC/nc12-atac.bw", format = 'bigWig')

export(nc13.atac.ba, con = "../Processed_Data/Wiggles/ATAC/WT_TC/nc13-atac.bw", format = 'bigWig')

export(nc14.atac.ba, con = "../Processed_Data/Wiggles/ATAC/WT_TC/nc14-atac.bw", format = 'bigWig')

export(lnc14.atac.ba, con = "../Processed_Data/Wiggles/ATAC/WT_TC/lnc14-atac.bw", format = 'bigWig')

```

## RNA-seq timecourse

Merged Samples by stage

```{r}
mtrnl.rna <- sort(unlist(wt.tc.rnaseq[1:4]))

nc11.rna <- sort(unlist(wt.tc.rnaseq[5:8]))

nc12.rna <- sort(unlist(wt.tc.rnaseq[9:12]))

nc13.rna <- sort(unlist(wt.tc.rnaseq[13:16]))

nc14.rna <- sort(unlist(wt.tc.rnaseq[17:20]))

lnc14.rna <- sort(unlist(wt.tc.rnaseq[21:24]))
```


Bin averages
```{r}

mtrnl.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(mtrnl.rna), varname = 'score')

nc11.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc11.rna), varname = 'score')

nc12.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc12.rna), varname = 'score')

nc13.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc13.rna), varname = 'score')

nc14.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(nc14.rna), varname = 'score')

lnc14.rna.ba <- binnedAverage(bins = ca.10bp, numvar = coverage(lnc14.rna), varname = 'score')

```

CPM Normalize
```{r}
score(mtrnl.rna.ba) <- signif(score(mtrnl.rna.ba)/length(mtrnl.rna)*1e+6, 4)

score(nc11.rna.ba) <- signif(score(nc11.rna.ba)/length(nc11.rna)*1e+6, 4)

score(nc12.rna.ba) <- signif(score(nc12.rna.ba)/length(nc12.rna)*1e+6, 4)

score(nc13.rna.ba) <- signif(score(nc13.rna.ba)/length(nc13.rna)*1e+6, 4)

score(nc14.rna.ba) <- signif(score(nc14.rna.ba)/length(nc14.rna)*1e+6, 4)

score(lnc14.rna.ba) <- signif(score(lnc14.rna.ba)/length(lnc14.rna)*1e+6, 4)
```


Export 
```{r}
stages <- c("mtnrl","nc11","nc12","nc13","nc14","lnc14")
export.path <- paste0("../Processed_Data/Wiggles/RNA/WT_TC/",stages,"-rna.bw")
export.path
```

```{r}
export(object = mtrnl.rna.ba, con = export.path[1], format = "bigWig")

export(object = nc11.rna.ba, con = export.path[2], format = "bigWig")

export(object = nc12.rna.ba, con = export.path[3], format = "bigWig")

export(object = nc13.rna.ba, con = export.path[4], format = "bigWig")

export(object = nc14.rna.ba, con = export.path[5], format = "bigWig")

export(object = lnc14.rna.ba, con = export.path[6], format = "bigWig")

```
